%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jonathan Cirillo Resume (As of 7/28/2023)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Used the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}

\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%\namesection {Jonathan}{Cirillo}
\namesection \LARGE {{Jonathan} {Cirillo}}{\href{https://cirillojon.herokuapp.com/}{cirillojon.herokuapp.com}}

\vspace{18pt}
\newfontfamily{\FA}{Font Awesome 5 Free}

\newcommand{\linkedin}[1]{\faLinkedin\hspace{0.5em}\href{https://linkedin.com/in/#1}{\texttt{#1}}}
\newcommand{\github}[1]{\faGithub\hspace{0.5em}\href{https://github.com/#1}{\texttt{#1}}}

% \faEnvelope\ \href{mailto:jonathancirillo@outlook.com}{jonathancirillo@outlook.com} \quad\textbullet\quad \faPhone\ 407.718.1174
{\FA \faEnvelope} {\href{mailto:jonathancirillo@outlook.com}{jonathancirillo@outlook.com}}\hspace{5pt}|\hspace{5pt}{\FA \faPhone} 407.718.1174 |\hspace{5pt} {\FA \faLinkedin} {\href{https://linkedin.com/in/jonathan-cirillo/}{linkedin}} \hspace{5pt}|\hspace{5pt} {\FA \faGithub} {\href{https://github.com/cirillojon}{github}}

\customsection{Education}

\runsubsection{University of Central Florida}
\descript{| B.S. in Computer Science}
\location{August 2019 - August 2023 | Orlando, FL }
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\customsection{Experience}

\runsubsection{F5 Networks}
\descript{| Software Engineer | Seattle, WA}
\descript{August 2023 – Present | Python, GitSwarm, Confluence}
\begin{tightemize}
\item Supporting F5's next-gen rSeries and VELOS Products as a member of the Velocity System Integration team.
\end{tightemize}
\sectionsep


\runsubsection{VS \& Co.}
\descript{| Software Engineer Intern | Remote}
\descript{May 2023 – August 2023 | Go, Azure, Kubernetes, Docker, CouchDB, MongoDB, Consul}
\begin{tightemize}
\item Member of VS Digital team supporting 100s of Go microservices within an Azure Kubernetes environment.
\item Optimized a core service’s performance by transitioning blacklisted user storage from array to map structure, achieving from 100x to 1000x faster data lookups. Leveraged CouchDB \& Consul for local testing of updates.
\end{tightemize}
\sectionsep

\runsubsection{VS \& Co.}
\descript{| Applications Developer Intern | Remote}
\descript{May 2022 – Apr 2023 | C\#, Java, SQL, Powershell, .NET, WPF, Bitbucket, Cherwell}
\begin{tightemize}
\item Investigated software issues affecting pin-pads in all North American Stores as a member of Payments team.
\item Utilized PowerShell for log processing \& conducted root cause analysis of bugs impacting millions of users.
\item Identified production faults with APIs and firewalls, saving the company from thousands in potential losses.
\item Aided in development of new Merchandise Planning Application, boosting productivity for hundreds of staff.
\item Created data in MS SQL for Quality Assurance testing of Planning App \& validated APIs using SwaggerHub.
\end{tightemize}
\sectionsep

\runsubsection{Informa Software}
\descript{| Software Engineer Intern | Maitland, FL}
\descript{Jan 2022 – May 2022 | JavaScript, C\#, Liquid Office, Budibase}
\begin{tightemize}
\item Created user-friendly forms \& business solutions for companies in diverse industries using JavaScript and C\#.
\item Led research into cloud-hosting solutions, which could potentially diminish existing hosting expenses by 35\%.
\item Produced comprehensive technical documentation, \& facilitated multiple meetings to demonstrate findings.
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\customsection{PROJECTS}

\runsubsection{Augmented Reality Cooking Simulator}
\descript{| 2023 }
\descript{Flutter, Dart, Unity, C\#, Firebase | Lead Backend Developer\hfill
\href{https://arcuttingboard.com/}{Link to Website}}
\begin{tightemize}
\item Engineered Dart \& C\# APIs for efficient app-to-database communication \& dynamic data presentation on UI.
\item Deployed open-source 'GLTFUtility' plugin for real-time instantiating of 3D assets from Firebase storage.
\item Conceptualized \& constructed a System Design Model that minimized DB requests saving thousands in costs.
\item Instituted user authentication using Google \& Facebook via Flutter \& Dart, ensuring Firebase data protection.
\end{tightemize}
\sectionsep

\runsubsection{Java Chess Engine \& Multi-threaded AI}
\descript{ |  2023 }
\descript{ Java, LaTeX, IntelliJ, Guava | Lead Developer \& Project Manager\hfill \href{https://cirillojon.herokuapp.com/images/Final-Paper.pdf}{Link to Paper}}
\begin{tightemize}
\item Developed a robust Java-based chess engine with a multi-threaded AI using alpha-beta-pruning. 
\item Presented research paper detailing 270\% performance increase achieved through paralellizing alpha-beta.
\end{tightemize}
\sectionsep

\runsubsection{Spotify Web/Mobile Application}
\descript{| 2022}
\descript{JavaScript, MongoDB, Express, React.js, Node.js | Project Manager\hfill \href{https://trendify-project.herokuapp.com/}{Link to Project}}
\begin{tightemize}
\item Spearheaded the creation of 'Trendify', a web and mobile application integrated with Spotify.
\item Leveraged Spotify's API, enabling users to synchronize their accounts and explore comprehensive listening data and track details. Technologies also employed include Jest, React Native, Android Studio, and Expo.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    TECHNICAL SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\customsection{Technical Skills}

\descript{Programming Languages:  Java \textbullet{} Python \textbullet{} Go \textbullet{}  C\# \textbullet{} C \textbullet{} JavaScript \textbullet{} SQL \textbullet{} Dart \textbullet{} LaTeX }  


\descript{Data Management \& Tools: Firebase \textbullet{} MongoDB \textbullet{} GitHub \textbullet{} Docker \textbullet{} MySQL \textbullet{} Azure \textbullet{} Kubernetes}
\descript{Libraries, Frameworks, \& IDEs: 
React.js \textbullet{} Node.js \textbullet{} Flutter \textbullet{}
Keras \textbullet{} .NET \textbullet{} Unity \textbullet{} VS Code \textbullet{} IntelliJ }
\sectionsep\
\hfill
\vfill\eject
\end{document} \documentclass[oneside]{article}
