%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jonathan Cirillo Resume (As of 5/29/2023)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Used the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}

\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%\namesection {Jonathan}{Cirillo}
\namesection \LARGE {{Jonathan} {Cirillo}}{\href{https://cirillojon.herokuapp.com/}{cirillojon.herokuapp.com}}

\vspace{18pt}
\newfontfamily{\FA}{Font Awesome 5 Free}

\newcommand{\linkedin}[1]{\faLinkedin\hspace{0.5em}\href{https://linkedin.com/in/#1}{\texttt{#1}}}
\newcommand{\github}[1]{\faGithub\hspace{0.5em}\href{https://github.com/#1}{\texttt{#1}}}

% \faEnvelope\ \href{mailto:jonathancirillo@outlook.com}{jonathancirillo@outlook.com} \quad\textbullet\quad \faPhone\ 407.718.1174
{\FA \faEnvelope} {\href{mailto:jonathancirillo@outlook.com}{jonathancirillo@outlook.com}}\hspace{5pt}|\hspace{5pt}{\FA \faPhone} 407.718.1174 |\hspace{5pt} {\FA \faLinkedin} {\href{https://linkedin.com/in/jonathan-cirillo/}{linkedin}} \hspace{5pt}|\hspace{5pt} {\FA \faGithub} {\href{https://github.com/cirillojon}{github}}

\customsection{Education}

\runsubsection{University of Central Florida}
\descript{| B.S. in Computer Science}
\location{Expected July 2023 | Orlando, FL }
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\customsection{Experience}

\runsubsection{VS \& Co.}
\descript{| Software Engineer Intern}
\location{May 2023 – Present | Remote}
\begin{tightemize}
\item Constructed scalable microservices using Go, Go-kit, \& Azure Kubernetes Services.
\item Utilized Docker \& NoSQL databases (CouchDB \& MongoDB) for optimal app portability \& data handling.
\item Employed Prometheus and Grafana for comprehensive system health tracking.
\item Facilitated cross-functional collaboration for seamless microservices integration across teams.
\end{tightemize}
\sectionsep

\runsubsection{Cutting Board (Startup)}
\descript{| Lead Backend Developer }
\location{January 2023 - Present | Orlando, FL \hfill \href{https://arcuttingboard.com/}{Link to Website}}
\begin{tightemize}
\item Established user auth with Google \& Facebook via Flutter \& Dart, safeguarding data in Firebase.
\item Deployed GLTFUtility for real-time 3D model loading from Firebase into AR scenes.
\item Developed C\# and Dart APIs for effective app-to-DB communication and data exchange.
\end{tightemize}
\sectionsep

\runsubsection{VS \& Co.}
\descript{| Applications Developer Intern }
\location{May 2022 – Apr 2023 | Remote}
\begin{tightemize}
\item Troubleshooted \& mitigated software issues affecting store pin-pads via PowerShell.
\item Identified and rectified production faults like malfunctioning APIs \& firewalls.
\item Aided in app development, testing, \& support for MP\&A team via C\# and .NET.
\item Prepared data in MSSQL for QA testing, validated APIs using SwaggerHub.
\end{tightemize}
\sectionsep

\runsubsection{Informa Software}
\descript{| Software Engineer Intern}
\location{Jan 2022 – May 2022 | Maitland, FL}
\begin{tightemize}
\item Created user-friendly forms \& business solutions for diverse industries using JavaScript and C\#.
\item Led research into cloud-hosting applications, reducing hosting costs by 35\%.
\item Authored technical documentation, \& led meetings to present findings.
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\customsection{PROJECTS}

\runsubsection{Java Chess Engine \& Multi-threaded AI}
\descript{ |  2023 }
\descript{ Java, LaTeX, IntelliJ, Guava \hfill \href{https://cirillojon.herokuapp.com/images/Final-Paper.pdf}{Link to Paper}}
\begin{tightemize}
\item Developed a robust Java-based chess engine with a multi-threaded AI using alpha-beta-pruning. 
\item Conducted research \& presented results detailing runtime improvements made by parallelizing alpha-beta.
\end{tightemize}
\sectionsep

\runsubsection{Mini-games Web app}
\descript{|  2023}
\descript{React.js, Unity, JavaScript, C\#, AWS Lambda, ThreeJS \hfill \href{https://react-app-sandbox.netlify.app/}{Link to Project}} 
\begin{tightemize}
\item Created app using React filled with various minigames inlcuding: snake, tic-tac-toe, \& a Unity WebGL game.
\end{tightemize}
\sectionsep

\runsubsection{Spotify Web/Mobile Application}
\descript{| 2022}
\descript{MongoDB, Express, React.js, Node.js \hfill \href{https://trendify-project.herokuapp.com/}{Link to Project}}
\begin{tightemize}
\item Led the development of a Spotify web and mobile application called ‘Trendify’
\item Utilized Spotify’s API to allow users to connect their account and view in-depth listening data \& track information. Other technology used: Jest, React Native, Android Studio, Expo, Lucidchart, and Heroku.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    TECHNICAL SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\customsection{Technical Skills}

\descript{Programming Languages:  Java \textbullet{} Go \textbullet{}  C\# \textbullet{} C \textbullet{} JavaScript \textbullet{} Python \textbullet{} SQL \textbullet{} Dart \textbullet{} LaTeX }  


\descript{Data Management \& Tools: MongoDB \textbullet{} Firebase \textbullet{} Docker \textbullet{} MySQL \textbullet{} Azure \textbullet{} GitHub  
\textbullet{} Jira \textbullet{} Kubernetes}
\descript{Libraries, Frameworks, \& IDEs: 
React.js \textbullet{} Node.js \textbullet{} Flutter \textbullet{}
Keras \textbullet{} .NET \textbullet{} Unity \textbullet{} VS Code \textbullet{} IntelliJ }
\sectionsep\
\hfill
\vfill\eject
\end{document} \documentclass[oneside]{article}
